quollr: An R Package for Visualizing 2D Models from Nonlinear Dimension Reductions in High Dimensional Space

### 2024-06-07 paper-quollr.Rmd
Added scratch for the algorithm writing

@@

```{r}
scaled_nldr_data <- gen_scaled_data(data = s_curve_noise_umap)

scaled_nldr_data
```

>>>>

The following demonstration of the package's functionality assumes `quollr` has been loaded. We also want to load the built-in data sets `s_curve_noise_training`, `s_curve_noise_test` and `s_curve_noise_umap`.

`s_curve_noise_training` is a $3-D$ S-curve dataset with additional four noise dimensions which is used to train the model. `s_curve_noise_test` is used for prediction. `s_curve_noise_umap` is the UMAP $2-D$ embedding for `s_curve_noise_training` dataset. Each dataset contains a unique ID column.

```{r, echo=TRUE}
scaled_nldr_obj_scurve <- gen_scaled_data(data = s_curve_noise_umap)

s_curve_noise_umap_scaled <- scaled_nldr_obj_scurve$scaled_nldr

lim1 <- scaled_nldr_obj_scurve$lim1
lim2 <- scaled_nldr_obj_scurve$lim2
r2 <- diff(lim2)/diff(lim1) 
```

The mains steps for the algorithm can be executed by the main function `fit_highd_model()`, or can be run separately for more flexibility. When constructing the 2D model, the user can choose either to fit the 2D model with hexagonal bin centroids or bin means using `is_bin_centroid` argument.

If a user would like to perform steps of the algorithm themselves, additional user input will be needed for the function that perform each step. For example, if the user wishes to use already binning data, the `extract_hexbin_centroids()` function can be used directly.

The number of bins along the x axis, the ratio of the ranges of the original embedding components, and if `is_rm_lwd_hex = TRUE`, benchmark value to remove low density hexagons are parameters that will be determined within `fit_highd_model`, if they are not provided. They are created as they are needed throughout the following example.

```{r, echo=TRUE}
fit_highd_model(
  training_data = s_curve_noise_training,
  emb_df = s_curve_noise_umap_scaled, 
  bin1 = 15, r2 = r2, 
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = TRUE,
  benchmark_to_rm_lwd_hex = NULL,
  col_start_highd = "x")
```

@@
